Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 14

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for fixed controls $u\equiv0$ and $\delta_u\equiv0$ for systems~\eqref{eq:general system} and \eqref{eq:general system:differential}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,0,0))\leq -\lambda V(x,\delta_x)
 	 	 \end{equation}
 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

>>>>

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t),\Delta(t))\leq -\lambda V(X(t),\Delta(t))
 	 	 \end{equation}
 	 	 holds, where $X(t):=X(t,x,u)$ and $\Delta(t):=\Delta(t,x,\delta_x,u,0)$, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}
